---
title: "quantifiedSelf Report"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

```{r, echo=FALSE}
source("script.R")
library("ggplot2")
library("knitr")
```

## Introduction

Recording, measuring and analysing personal drug consumption; including medicinal and recreational/habitual.

### The data

Base data includes (of the observation) the date and time, location (postcode), and the activity being recorded.

## Analysis

Here is a very quick plot of the data.

```{r}
with(selfData, qplot(DateTime, Activity, alpha=I(0.25)))
```

And totals for each activity. 

```{r}
for (i in 1:length(levels(as.factor(selfData$Activity)))) {
  print(paste(colnames(dailyTotals)[i],":",sum(dailyTotals[,i])))
}
```

### Consumption by weekdays

By grouping daily consumption and then averaging across weekdays, the below plot shows something like how an average week of consumption looks.

```{r}
ggplot(wdayAvg, aes(x = Weekday, y = Average, color = Activity, group = Activity)) + 
    geom_point() + 
    geom_line()
```

### Weekly intake

```{r}
kable(weekAvg)
```

### iOS Health/Activity cross-examination

Merging physical activity data can show some correlations with certain kinds of consumption. Here, active (non-basal) calorie burning is plotted against consumption categories.

**Commented out**

```{r, echo=FALSE}
#source("activity.R")
```

```{r}
#qplot(kcals, value, data = activityVsConsumption, facets = .~variable, alpha=I(0.25)) + 
#    geom_smooth(method = "lm")
```